---
title: "Why I use Knitr/Markdown"
author: "John Muschelli"
date: "July 28, 2015"
output: ioslides_presentation
---

```{r results='hide', echo=FALSE}
rinline <- function(code) { sprintf('<code class="r">```  ```</code>', code) }
```
## RMarkdown/LaTeX/pandoc


- LaTeX and RMarkdown are types of **markdown**
- pdflatex/pandoc are engines/interpreters that take the markdown to another format
  - pdflatex makes PDFs 
    - $\LaTeX \xrightarrow{pdflatex} \text{ PDF}$
  - [pandoc](http://pandoc.org/) can convert almost any type of markdown to any other format
    - think markdown to a pdf/html/Word document
      - $\text{md} \xrightarrow{pandoc} \text{ Whatever}$


## Knitr/Sweave

- Sweave (pronounced S-weave or sweave) is a parser that takes LaTeX/TeX (not other types of markdown) and embedded code
  - Sweave creates a LaTeX/TeX document that has that code and it's output formatted for LaTeX/TeX
- Filename extensions are usually `Rnw`/`rnw` or maybe `.Rtex`

## Knitr Example

Example:
```
<<echo=FALSE, label="I am a code chunk">>=
## we are not in R code
x = 5
print(x)
# we stop the Sweave with an @ symbol (obviously right?)
@
I am in LaTeX and I want to say that my variable x is \Sexpr{x}.
```

## Knitr/Sweave

- Knitr (knit-R or "neater", though everyone goes with knit-r) is an extension of Sweave.
  - It can handle LaTeX
  - It can handle markdown, specifically RMarkdown (which is a dialect of generic markdown)
  - Filename extensions are usually `Rmd`/`rmd` 
  

## Knitr Example

Example:
```{r, results='hide', echo=FALSE}
x = 5 
```

```{r, results='asis', echo=FALSE}
cat(paste0('<pre class="lang-r">\n```{r echo=FALSE, label="I am a code chunk"}\n', 
"## we are not in R code\n", "x = 5\n", "print(x)\n", "# we stop the knitr with 3 backticks \n```\n</pre>"))
```

I am in Rmarkdown and I want to say that my variable x is `r x`.

## Plots work (may need to resize)

```{r, message=FALSE}
library(fslr)
t1 = readnii("JHU_MNI_SS_T1_brain.nii.gz")
ortho2(t1)
```



## Tables work (xtable package helpful)

```{r, message=FALSE, results='asis'}
tab = table(c(t1))
library(xtable)
xtab = xtable(tab)
print.xtable(xtab, type = "html")
```

